Pangenome graph layout by HOGWILD! Path-Guided Stochastic Gradient Descent

### 2023-06-28 manuscript/main.tex
more compact and less jargony abstract

	\abstract{
	\textbf{Motivation:}
	The increasing availability of high quality genomes demands models that allow for the study of genomic variability within entire populations.
	Pangenome graphs can represent the full genetic diversity between multiple genomes, but they may exhibit complex structures due to common, nonlinear patterns of genome variation and evolution.
	These structures introduce difficulty in downstream analyses, visualization, and interpretation. \\
	\textbf{Results:}
	To address these challenges, we propose a novel layout algorithm, the Path-Guided Stochastic Gradient Descent (PG-SGD).
	Our HOWGWILD! method uses the path position information of the genomes represented in the pangenome graph to move pairs of nodes in parallel.
	We demonstrate that our implementation can efficiently compute the latent structure of gigabase-scale pangenome graphs, revealing their biological features. \\
	\textbf{Availability:}
	The PG-SGD algorithm has been integrated in \textit{ODGI} which is released as free software under the MIT open source license.
	Source code is available at \url{https://github.com/pangenome/odgi} and documentation at \url{https://odgi.readthedocs.io/en/latest/rst/tutorials/sort_layout.html}. \\
	\textbf{Contact:} \href{egarris5@uthsc.edu}{egarris5@uthsc.edu} \\
	\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.
	}

>>>>

	\abstract{
	\textbf{Motivation:}
	The increasing availability of high quality genomes demands models to study genomic variability within entire populations.
	Pangenome graphs can represent the full genetic diversity between multiple genomes, but they may exhibit complex structures due to common, nonlinear patterns of genome variation and evolution.
	These structures introduce difficulty in downstream analyses, visualization, and interpretation. \\
	\textbf{Results:}
	To address these challenges, we propose a novel graph layout algorithm, the Path-Guided Stochastic Gradient Descent (PG-SGD).
	Our HOWGWILD! method uses the genomes, represented in the pangenome graph as paths, to move pairs of nodes in parallel.
	We show that our implementation efficiently computes the layout of gigabase-scale pangenome graphs, revealing their biological features. \\
	\textbf{Availability:}
	The PG-SGD algorithm has been integrated in \textit{ODGI} which is released as free software under the MIT open source license.
	Source code is available at \url{https://github.com/pangenome/odgi}. \\ % and documentation at \url{https://odgi.readthedocs.io/en/latest/rst/tutorials/sort_layout.html}. \\
	\textbf{Contact:} \href{egarris5@uthsc.edu}{egarris5@uthsc.edu} \\
	\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.
	}
